random forest and lme

### 2020-04-13 src/modelling - 550/rf.Rmd
changed doc to reflect changing avg to median and factors in mill rate and assessment data, and redid outputs used in final latex report to relfect this

lme.mill <- lmer(mill.rate ~ 1+ (1+year|municipality) + as.factor(year) + tax.class  + total.assessment + past.mill, data = train)

@@

lme.as <- lmer(next.assess ~ 1+ (1+year|municipality) + as.factor(year) + tax.class + total.assessment + mill.rate, data = train)

>>>>

lme.mill <- lmer(mill.rate ~ 1+ (1+year|municipality) + as.factor(year) + tax.class  + avg_assessment + past.mill, data = train_mill)

@@

lme.as <- lmer(next.assess ~ 1+ (1+year|municipality) + as.factor(year) + tax.class + total.assessment + mill.rate, data = train_as)
